Title Goes Here

### 2024-03-07 analysis/paper/paper.qmd
explore smoothing on topic time trends

ggplot() +
  geom_line(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
            position=position_jitter(w=0.05, h=0.0)) +
  geom_point(data = jobdata_topic_year_tally_max,
             aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
             size = 10) +
  geom_text_repel(data = jobdata_topic_year_tally_max,
                  aes(year_ad_posted,
                      prop ,
                      group = name,
                      colour = name,
                      label = name),
                  nudge_y = 0.01,
                  bg.color = "white",
                  bg.r = 0.25,
                  size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

>>>>

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
            position=position_jitter(w=0.05, h=0.0),
            se = FALSE) +
  geom_point(data = jobdata_topic_year_tally_max,
             aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
             size = 10) +
  geom_text_repel(data = jobdata_topic_year_tally_max,
                  aes(year_ad_posted,
                      prop ,
                      group = name,
                      colour = name,
                      label = name),
                  nudge_y = 0.01,
                  bg.color = "white",
                  bg.r = 0.25,
                  size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()
